CS182: NBA Scheduler

### 2015-12-10 paper.tex
remove heuristics word
Making required changes in the paper

	\subsection{Methodology for the roundwise schedule}
	We create a variable for every team against every other team, for every round. The first part of the variable is the home team followed by the away team and the round number. We introduce the following constraints to the ILP
	\begin{enumerate}
		\item All teams play 82 games, 41 home and away
		\item All constraints for the division, in conference and out of conference teams
		\item No team can play more than one game in a round
		\item Team can only play either home or away
	\end{enumerate}
	The above ILP was solved using the PuLP as well as the GUROBI solver. The PuLP solver took 40 minutes to converge to solution whereas the GUROBI solver took 6 seconds on average. The schedule was verified using tests to check if all constraints were satisfied.

	\subsection{Generating the player friendly schedule}
	Using the dates generated by datagen, we formulated the ILP for a player friendly schedule. The variables are created for every date instead of every round.  To reduce the number of variables we generate the variables for every possible home and away dates only. This reduces the number of variables by about 70\%. The time taken to create the constraints and to solve the ILP are greatly reduced. We use the following constraints.
	\begin{enumerate}
		\item All teams play 82 games, 41 home and away
		\item All constraints for the division, in conference and out of conference teams
		\item No team can play more than one game on a single date
		\item Team can only play either home or away
		\item A team can only play 3 or lesser matches in 5 days
		\item A team does not play 2 away games without a day's break
		\item A team does not play an away game right after a home game
	\end{enumerate}
	The above ILP was solved using the PuLP as well as the GUROBI solver. The PuLP solver took 1 hour to converge to solution whereas the GUROBI solver took 29 seconds on an average. In some cases the 4 games in 5 days was unavoidable due to mismatch in dates, but our solution aimed to minimize it.

@@

	\section{Work Distribution}
	\begin{itemize}
	\item Data Generation - Charles created the structure of the league as well as the initial data generation class. As the project progressed changes were made by all members.
	\item ILP - Sam and Abhishek worked on the initial matchups problem. From there, Abhishek took the lead on solving home/away's and dates as well as moving to the faster GUROBI.
	\item CSP - Charles created the general structure of the scheduler/domain/constraint files and the sub-CSP problems. From there the more involved work (heuristics, testing) were split as follows:
		\begin{itemize}
			\item Matchups heuristics - Charles
			\item Home/Aways heuristics - Charles and Sam pair coded
			\item Dates/UCS - primarily Sam with some input on cost functions from Charles
		\end{itemize}
	\end{itemize}

>>>>

	\subsection{Methodology for the roundwise schedule}
	We create a variable for every team against every other team, for every round. In this part of the problem, we assume that there are 15 games every round with every team playing in that particular round. The first part of the variable is the home team followed by the away team and the round number.

	\begin{eqnarray*}
		variable : (Home \ Team, Away \ Team, Round \ Number)
	\end{eqnarray*}

	We introduce the following constraints to the ILP.
	\begin{enumerate}
		\item All teams play 82 games, 41 home and away
		\item All constraints for the division, in conference and out of conference teams
		\item No team can play more than one game in a round
		\item Team can only play either home or away
	\end{enumerate}
	The above ILP was solved using the PuLP as well as the GUROBI solver. The PuLP solver took 40 minutes to converge to solution whereas the GUROBI solver took 6 seconds on average. The schedule was verified using tests to check if all constraints were satisfied.

	\subsection{Generating the player friendly schedule}
	Using the dates generated by datagen, we formulated the ILP for a player friendly schedule. The variables are created for every date instead of every round.  To reduce the number of variables we generate the variables for every possible home and away dates only. For every team, we create the variables for every home date for every opposition. Similarly, we create the variables for every away date for a particular opponent.

	\begin{eqnarray*}
		variable : (Home \ Team, Away \ Team, Game \ Date)
	\end{eqnarray*}

	This reduces the number of variables by about 70\%. The time taken to create the constraints and to solve the ILP are greatly reduced. We use the following constraints.
	\begin{enumerate}
		\item All teams play 82 games, 41 home and away
		\item All constraints for the division, in conference and out of conference teams
		\item No team can play more than one game on a single date
		\item Team can only play either home or away
		\item A team can only play 3 or lesser matches in 5 days
		\item A team does not play 2 away games without a day's break
		\item A team does not play an away game right after a home game
	\end{enumerate}
	The above ILP was solved using the PuLP as well as the GUROBI solver. The PuLP solver took 1 hour to converge to solution whereas the GUROBI solver took 29 seconds on an average. In some cases the 4 games in 5 days was unavoidable due to mismatch in dates, but our solution aimed to minimize it.

@@

	\section{Work Distribution}
	\begin{itemize}
	\item Data Generation - Charles created the structure of the league as well as the initial data generation class. As the project progressed changes were made by all members.
	\item ILP - Sam and Abhishek worked on the initial matchups problem. From there, Abhishek took the lead on solving home/away's and dates as well as moving to the faster GUROBI.
	\item CSP - Charles created the general structure of the scheduler/domain/constraint files and the sub-CSP problems. From there the more involved work (heuristics, testing) were split as follows:
		\begin{itemize}
			\item Matchups - Charles
			\item Home/Aways - Charles and Sam pair coded
			\item Dates/UCS - primarily Sam with some input on cost functions from Charles
		\end{itemize}
	\end{itemize}
